13th International Satisfiability Modulo Theories Competition (SMT-COMP 2018): Rules and Procedures

### 2018-04-19 rules/rules18.tex
More detailed discussion of time limit

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
  Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2018.  The principal changes from the previous competition
rules are the following:
\begin{itemize}
\item The organizers plan to recognize additional special
  contributions.  These might include:
  \begin{itemize}
  \item Best application track solver (awarded based on a
    competition-wide scoring for the application track)
  \item Best unsat-core track solver (awarded based on a
    competition-wide scoring for the unsat-core track)
  \item Best complementary solver (awarded to the solver that performs
    best when all benchmarks solved by the winning solver are removed)
  \item Most unique solver (awarded to the solver that performs best
    on benchmarks solved by only one solver)
  \item The Prophet (awarded to the solver that performs best on
    benchmarks with unknown status)
  \item The 10 Second Wonder (awarded to the solver that would have
    won if the time limit was 10 seconds)
  \end{itemize}
  The details are still being discussed and subject to change.
\item In the unsat-core track, the unsatisfiability check for the
  returned core will be based on a simple majority vote.  The case
  that a solver finds its own core satisfiable will no longer be
  treated specially.  \emph{Rationale:} This allows to simplify the
  post-processing of unsat-core track results considerably.

@@

\header{Wrapper tools.}
%
A \emph{wrapper tool} is defined as any solver which calls (or is in
some other way based on) one or more SMT solvers not written by the
author of the wrapper tool.  The other solvers are called the
\emph{wrapped} solvers.  A wrapper tool must explicitly acknowledge
any solvers that it wraps.  Its system description should make clear
the technical innovations by which the wrapper tool expects to improve
on the wrapped solvers.

@@

The time limit~$T$ is yet to be determined, but it is anticipated to
be at most 20~minutes of wall-clock time per solver/benchmark
pair.\footnote{The time limit may be adjusted once we know the number
  of competition entrants and eligible benchmarks.}  Solvers that take
more than this time limit will be killed.  Solvers are allowed to
spawn other processes; these will be killed at approximately the same
time as the first started process.

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
  Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2018.  The principal changes from the previous competition
rules are the following:
\begin{itemize}
\item The organizers plan to recognize additional special
  contributions.  These might include:
  \begin{itemize}
  \item Best application track solver (awarded based on a
    competition-wide scoring for the application track)
  \item Best unsat-core track solver (awarded based on a
    competition-wide scoring for the unsat-core track)
  \item Best complementary solver (awarded to the solver that performs
    best when all benchmarks solved by the winning solver are removed)
  \item Most unique solver (awarded to the solver that performs best
    on benchmarks solved by only one solver)
  \item The Prophet (awarded to the solver that performs best on
    benchmarks with unknown status)
  \item The 10 Second Wonder (awarded to the solver that would have
    won if the time limit was 10 seconds)
  \end{itemize}
  The details are still being discussed and subject to change.

\item The time limit per solver/benchmark pair is anticipated to be at
  most 20 minutes in the main track, and at most 40 minutes in the
  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
  the main track was reduced to 20 minutes (down from 40 minutes in
  earlier years) to cope with the inclusion of a large number of
  benchmarks with unknown status.

\item In the unsat-core track, the unsatisfiability check for the
  returned core will be based on a simple majority vote.  The case
  that a solver finds its own core satisfiable will no longer be
  treated specially.  \emph{Rationale:} This allows to simplify the
  post-processing of unsat-core track results considerably.

@@

\header{Wrapper tools.}
%
A \emph{wrapper tool} is defined as any solver that calls (or is in
some other way based on) one or more SMT solvers not written by the
author of the wrapper tool.  The other solvers are called the
\emph{wrapped} solvers.  A wrapper tool must explicitly acknowledge
any solvers that it wraps.  Its system description should make clear
the technical innovations by which the wrapper tool expects to improve
on the wrapped solvers.

@@

The time limit~$T$ is yet to be determined.  It is anticipated to be
at most 20~minutes of wall-clock time per solver/benchmark pair in the
main track, and at most 40~minutes in the other tracks.\footnote{The
  time limit may be adjusted once we know the number of competition
  entrants and eligible benchmarks.}  Solvers that take more than this
time limit will be killed.  Solvers are allowed to spawn other
processes; these will be killed at approximately the same time as the
first started process.
